---
title: "Analysis of SARS-CoV-2 concentration in wastewater"
author: "Yawei"
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: hide
    toc: true
    toc_float: true
hitheme: tomorrow
highlighter: highlight.js
---

```{r setup, include=FALSE}
library(tidyverse)
library(here)
knitr::opts_chunk$set(echo = TRUE,
  warning = FALSE,
  message = FALSE,
  fig.width = 9,
  fig.height = 8,
  fig.path = "../results/"
)
theme_set(theme_bw() + theme(legend.position = "bottom"))

```

## Overview
```{r, include = FALSE}
download_date = Sys.Date()
```



## Download and clean data
Two data sources were pulled and merged for this analysis. One is a dataset of SARS-CoV-2 wastewater concentration at different sampling sites, which can be accessed [here](https://data.cdc.gov/Public-Health-Surveillance/NWSS-Public-SARS-CoV-2-Concentration-in-Wastewater/g653-rqe2/about_data). The second, accessible [here](https://data.cdc.gov/Public-Health-Surveillance/NWSS-Public-SARS-CoV-2-Wastewater-Metric-Data/2ew6-ywp6/about_data), contains summary information about SARS-CoV-2 wastewater concentration at different sites, with additional information about site location including county and state.
First we downloaded and cleaned the data from the CDC website. 


```{r}
source(here("source", "01_data_download.R"))
source(here("source", "02_data_cleaning.R")) 
```


## Analysis

```{r}
source(here("source", "03_data_analysis.R"))
```


```{r}
covid_table %>%
  knitr::kable()
```


# Visualization
Finally, we visualize the concentration across counties. 
```{r}
source(here("source", "04_data_visualization.R"))
```


```{r, boxplot}
plot1
```
Next, we visualize trends in SARS-CoV-2 concentration over time.
```{r, lineplot, fig.height = 10}
plot2
```

